---
title: "Data Analysis with Visuals using R"
author: "Abdulwahid"
date: "4/21/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Load libraries
The libraries contain functions that will be used for accessing various visuals.The library used is ggplot2 a famous visualization based library.
```{r}
library("ggplot2")
```

## The number of people who consume Alcohol daily
* Around 40 people consume 0-79g of alcohol daily in Ille-et-Vilaine, France
* Less than 20 people consume 80-119g of alcohol daily
* About 5 people consume 120+ grams of alcohol daily
```{r esoph}
ggplot(esoph, aes(x=ncontrols, y=alcgp))+
  theme_bw()+
  geom_boxplot()+
  labs(y="Alcohol consumption",
       x="Number of controls",
       title="Number of controls(no cancer) based on alcohol")
```

## The age groups of people who consume tobacco daily
* Age range of 25-34 consume 30+ grams of tobacco daily in Ille-et-Vilaine, France
* Age range of 35-44,45-54,55-64,65-74 consume less tobacco of about 20-30 grams daily
* Age range of 75+ consume 30+ grams of tobacco daily on very high density
```{r}
ggplot(esoph, aes(x=ncases, fill=tobgp))+
  theme_bw()+
  facet_wrap(~agegp)+
  geom_density(alpha=0.5)+
  labs(x="Number of of cases",
       title="Tobacco consumption based on age groups")
```

## The age groups of people who consume alcohol daily
* Age range of 25-34, 35-44 consume similar levels of alcohol daily in Ille-et-Vilaine, France
* Age range of 45-54,55-644 consume more alcohol compared to other groups
* Age range of 75+ consume the least alcohol compared to others
```{r}
ggplot(esoph, aes(x=agegp, fill=alcgp))+
  theme_bw()+
  geom_bar()+
  labs(x="Age group",
       y="Alchohol count",
       title="Alchohol consumption based on Age")
```
